Knowledge-based Detection of Arabic Entity Graphs using Morphology and Graph Transformations

### 2011-11-04 tex/cicling.tex
updated some issues to make SUBMISSION version suitable for use with no reliance on database and corrected some minor issues

\begin{table*}[bt]                                     
\centering                                            
\caption{Results comparing between NaGEMA and iTree.}
\resizebox{2.1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
%\multicolumn{13}{c}{NaGEMA with all refinements} \\ \cline{3-13}
& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{NaGEMA }&musnad & & 0.999 & 0.999 & 0.999 & & 0.993 & 0.990 & 0.991 & & 0.999 & 0.998 & 0.999 \\
&kafi & & 0.999 & 0.920 & 0.958 & & 0.937 & 0.970 & 0.953 & & 0.993 & 0.988 & 0.990 \\
&istibsar & & 0.999 & 0.973 & 0.986 & & 0.980 & 0.950 & 0.965 & & 0.996 & 0.998 & 0.997 \\ \cline{2-14}
& & & 0.999 & 0.964 & 0.982 & & 0.970 & 0.970 & 0.970 & & 0.996 & 0.995 & 0.995 \\ \hline \hline
%& & &  &  &  & &  &  &  & &  &  & \\
%&\multicolumn{13}{c}{iTree} \\ \cline{3-13}
& & & \multicolumn{3}{c}{accept as hadith} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{iTree} &musnad & & 0.999 & NA & 0.999 & & 0.997 & 0.977 & 0.987 & & 0.998 & 0.999 & 0.999  \\
&kafi & & 0.043 & NA & 0.083 & & 0.999 & 0.313 & 0.476 & & 0.999 & 0.999 & 0.999 \\
&istibsar & & 0.028 & NA & 0.054 & & 0.875 & 0.583 & 0.700 & & 0.999 & 0.999 & 0.999 \\ \cline{2-14}
& & & 0.357 & NA & 0.379 & & 0.957 & 0.624 & 0.721 & & 0.999 & 0.999 & 0.999 \\ 
 \end{tabular}                 
}                             
\normalsize                   
\label{t:hadithresults} 
\end{table*}

@@

\begin{table*}[bt]                                     
\centering                                            
\caption{Results without punctuation and without learning. }
\resizebox{2.1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{no punctuation} 
& musnad  & & 0.999 & 0.999 & 0.999 & & 0.982 & 0.955 & 0.968 & & 0.999 & 0.998 & 0.999 \\ 
& kafi & & 0.999 & 0.793 & 0.885 & & 0.944 & 0.967 & 0.955 & & 0.996 & 0.938 & 0.966 \\
& istibsar & & 0.999 & 0.999 & 0.999 & & 0.980 & 0.931 & 0.955 & & 0.994 & 0.985 & 0.990 \\  \cline{2-14}
& &  & 0.999 & 0.931 & 0.962 & & 0.969 & 0.951 & 0.960 & & 0.997 & 0.974 & 0.985 \\ \hline \hline
%& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
%& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{no learning}
& musnad & & 0.999 & 0.999 & 0.999 & & 0.894 & 0.985 & 0.937 & & 0.995 & 0.999 & 0.998\\
& kafi & & 0.999 & 0.920 & 0.958 & & 0.937 & 0.970 & 0.953 & & 0.993 & 0.991 & 0.992\\
& istibsar & & 0.999 & 0.973 & 0.986 & & 0.977 & 0.950 & 0.963 & & 0.996 & 0.998 & 0.997\\ \cline{2-14}
 & &  & 0.999 & 0.964 & 0.982 & & 0.936 & 0.968 & 0.951 & & 0.995 & 0.996 & 0.995 \\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:nopunctlearnresults} 
\end{table*}

>>>>

\begin{table*}[bt]                                     
\centering                                            
\caption{Results comparing between NaGEMA and iTree.}
\resizebox{1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
%\multicolumn{13}{c}{NaGEMA with all refinements} \\ \cline{3-13}
& & & hadith & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & count & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-16}
\multirow{3}{*}{NaGEMA }
&musnad & & 212 & & 0.986 & 0.976 & 0.981 & & 0.969 & 0.967 & 0.968 & & 0.999 & 0.996 & 0.998 \\
&kafi & & 199 & & 0.970 & 0.909 & 0.938 & & 0.934 & 0.954 & 0.944 & & 0.999 & 0.998 & 0.998 \\
&istibsar  & & 189 & & 0.968 & 0.973 & 0.971 & & 0.946 & 0.945 & 0.945 & & 0.999 & 0.998 & 0.999 \\ \cline{2-16}
& & & 600 & & 0.975 & 0.953 & 0.964 & & 0.950 & 0.956 & 0.953 & & 0.999 & 0.997 & 0.998 \\ \hline \hline
%& & &  &  &  & &  &  &  & &  &  & \\
%&\multicolumn{13}{c}{iTree} \\ \cline{3-13}
& & & hadith & & \multicolumn{3}{c}{accept as hadith} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & count & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-16}
\multirow{3}{*}{iTree} 
&musnad && 62 && 0.999 & NA & NA & & 0.997 & 0.977 & 0.987 & & 0.998 & 0.999 & 0.999  \\
&kafi && 23 && 0.043 & NA & NA & & 0.999 & 0.313 & 0.476 & & 0.999 & 0.999 & 0.999 \\
&istibsar && 36 && 0.028 & NA & NA & & 0.875 & 0.583 & 0.700 & & 0.999 & 0.999 & 0.999 \\ \cline{2-16}
& & & 124 && 0.357 & NA & NA & & 0.957 & 0.624 & 0.721 & & 0.999 & 0.999 & 0.999 \\ 
 \end{tabular}                 
}                             
\normalsize                   
\label{t:hadithresults} 
\end{table*}

@@

\begin{table*}[bt]                                     
\centering                                            
\caption{Inter-annotator Agreement}
\resizebox{1\columnwidth}{!}{
\begin{tabular}{p{2cm}p{.1cm}cccp{.1cm}cccp{.1cm}ccc}
\multirow{2}{*}{Test Case} & &  \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad/genealogy boundary}  & &  \multicolumn{3}{c}{name boundary} \\
 & &  recall & precision & average & & recall & precision & average & & recall & precision & average \\ \cline{2-13}
Hadith &  & 0.976 & 1.000 & 0.988 & & 0.991 & 0.971 & 0.981 & & 1.000 & 0.997 & 0.999 \\ 
Genealogy &  &  1.000 & 0.390 & 0.695 & & 0.969 & 0.954 & 0.812 & & NA & NA & NA\\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:interannotator} 
\end{table*}

\begin{table*}[bt]                                     
\centering                                            
\caption{POR and Name Learning Results}
\resizebox{1\columnwidth}{!}{
\begin{tabular}{cp{1cm}c}
	\begin{tabular}{p{2.5cm}p{.1cm}ccc}
								& & recall & precision & F-score \\ \cline{2-5}
	All Narrators & &  0.632 & 0.771 & 0.694\\
	Detected Narrators & & 0.673 & 0.824 & 0.741\\
	\multicolumn{5}{c}{(a) Narrator POR Accuracy} \\
	\end{tabular}  
&  &
	\begin{tabular}{p{2cm}p{.1cm}ccc}
								& & recall & precision & F-score \\ \cline{2-5}
	Sanad Names & &  0.649 & 0.940 & 0.768\\
	All Names & & 0.794 & 0.733 & 0.762\\
	\multicolumn{5}{c}{(b) Name Learning Accuracy} \\
	\end{tabular}  \\
 \end{tabular}               
}                             
\normalsize                   
\label{t:PORnLearning} 
\end{table*}

\begin{table*}[bt]                                     
\centering                                            
\caption{Results comparing Narrator Detection Accuracy in Hadith and Biography}
\resizebox{1\columnwidth}{!}{

\begin{tabular}{cp{0.5cm}c}

	\begin{tabular}{p{2.5cm}cp{.1cm}cccp{.1cm}ccc}
	& & & \multicolumn{3}{c}{detection} & &  \multicolumn{3}{c}{boundary} \\
	& reported narrators& & recall & precision & F-score & & recall & precision & F-score \\ 
	\cline{2-2} \cline{4-10}
	\multirow{2}{*}{Hadith (musnad)}
	& of sanad & & 0.923 & 0.999 & 0.960 & & 0.996 & 0.999 & 0.998  \\
	& all & & 0.954 & 0.961 & 0.958 & & 0.996 & 0.987 & 0.992 \\ 
	\hline \hline
	\multirow{2}{*}{Biography (khoei)} 
	& found in POR & & 0.654 & 0.909 & 0.760 & & 0.933 & 0.960 & 0.946 \\
	& all & & 0.943 & 0.812 & 0.873 & & 0.407 & 0.945 & 0.569 \\
	 \end{tabular}   
&  &
	\begin{tabular}{cc}
	\multicolumn{2}{c}{narrator statistics} \\
	concentration & aggregation \\ \hline
	\multirow{2}{*}{0.217} &\multirow{2}{*}{ 2.64}\\ \\
	\hline \hline
	\multirow{2}{*}{0.489} & \multirow{2}{*}{3.54}\\
	\\
	\end{tabular}  \\
\end{tabular}          
}                             
\normalsize                   
\label{t:narratorDifference} 
\end{table*}

\begin{table*}[bt]                                     
\centering                                            
\caption{Biography Detection Results}
\resizebox{0.25\columnwidth}{!}{
	\begin{tabular}{p{2.5cm}p{.1cm}c}
	Exact Recall & &  0.6 \\
	Partial Recall & & 0.8\\
	Search Count & & 10 \\
	\end{tabular}             
}                             
\normalsize                   
\label{t:biography} 
\end{table*}

\begin{table*}[bt]                                     
\centering                                            
\caption{Results for Biblical Genealogy Parsing}
\resizebox{0.7\columnwidth}{!}{
\begin{tabular}{p{2.5cm}cccp{.1cm}ccc}
 & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{names extraction} \\
 &  recall & precision & F-score & & recall & precision & F-score \\ \cline{2-8}
basic controller & 0.796 & 0.708 & 0.749 & & 0.883 & 0.906 & 0.894 \\
refined controller & 0.796 & 0.742 & 0.768 & & 0.887 & 0.910 & 0.898 \\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:genealogyParsing} 
\end{table*}

\begin{table*}[bt]                                     
\centering                                            
\caption{Results for Biblical Genealogy Kinship Graphs}
\resizebox{1\columnwidth}{!}{
\begin{tabular}{p{2.5cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
& & & \multicolumn{3}{c}{available nodes} & &  \multicolumn{3}{c}{neighborhood} & &  \multicolumn{3}{c}{context} \\
& & &  recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{4-14}
\multirow{3}{*}{Basic Controller}
&Local Graphs && 0.583 & 0.898 & 0.707 && 0.778 & 0.760 & 0.769 && 0.552 & 0.588 & 0.570 \\
&Local Graphs (Aligned) && 0.849 & 0.868 & 0.858 && 0.777 & 0.738 & 0.757 && 0.554 & 0.590 & 0.572 \\
&Global Graph && 0.784 & 0.800 & 0.792 && 0.652 & 0.652 & 0.652 && 0.536 & 0.573 & 0.554  \\
\hline \hline
\multirow{3}{*}{Refined Controller}
&Local Graphs && 0.586 & 0.900 & 0.710 && 0.780 & 0.725 & 0.751 && 0.557 & 0.577 & 0.567 \\
&Local Graphs (Aligned) && 0.854 & 0.871 & 0.862 && 0.785 & 0.723 & 0.753 && 0.582 & 0.600 & 0.591 \\
&Global Graph && 0.820 & 0.810 & 0.815 && 0.701 & 0.708 & 0.704 && 0.580 & 0.630 & 0.604  \\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:genealogyGraphs} 
\end{table*}      .

\begin{table*}[bt]                                     
\centering                                            
\caption{Statistics for Biblical Genealogy Kinship Graphs}
\resizebox{0.7\columnwidth}{!}{
\begin{tabular}{p{1.5cm}lp{.1cm}ccccp{.1cm}c}
& & & \multicolumn{6}{c}{Node Count} \\ \cline{4-9}
& & & \multicolumn{4}{c}{Local Graphs} & & \multicolumn{1}{c}{Global Graph}\\
& Controller & &  minimum & average & maximum & total size & & size \\ \cline{2-9}
\multirow{2}{*}{Extracted}
&Basic && 3 & 7.89 & 35 & 513 && 245 \\
&Refined && 3 & 8.00 & 35 & 496 && 253 \\
 \hline
\multirow{1}{*}{Annotation}
&  && 2 & 8.80 & 77 & 475 && 250 \\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:genealogyGraphStatistics} 
\end{table*}
